
     
     Testing on 17 real videos demonstrates accuracy of \comment{[XX] TP} and \comment{[XX] FP} rates which is \comment{[XX]\%} improvement over prior method. Testing of 42 real images demonstrates 38\% improvement over prior method. %Note that the evaluation of the method is conducted at the 
    
    \begin{enumerate}
    \item Leveraging the scanning pattern of the video
    \item Learning features from a large set of images using convolutional neural network.
    \end{enumerate}
    
    
    
    \paragraph{Related Works}
        Much of the previous research in automatic crack detection has focused on developing a trained classifier using some hand-crafted features. For instance, 
        
        
        
        To reduce false positives, statistical features such as seed growing \cite{Li2011} and crack saliency \cite{Xu2013} have also been applied. 
        
        
        Jahanshahi et al. segment line-like segments using morphological operations, extract geometric features from the segments and then use a neural network classifier to determine if the segment is a crack \cite{jahanshahi2013}. A block SVM classifier with Hough features was used to detect cracks in noisy images HTF-SVM \cite{Hu2010}. Oliveira et. al develop a system to detect road cracks using an unsupervised learning method \cite{Oliveira2014}. Gabor features along with an Adaboost classifier are used to detect road cracks \cite{Medina2014}. Chanda et. al  detect cracks in highly textured bridges using texture features and SVM \cite{chanda2014}. Kapela et. al. detect asphalt using HOG and a SVM classifier \cite{Kapela2015}. Prasanna et. al. divide the image into blocks, detect lines using RANSAC in each block, extract gradient and intensity features from the block at different scales and then classify the block as crack or not using a classifier \cite{Prasanna2014}. Zou et. al detect defects in weld pipe inspection videos by using a Kalman filter to detect the continuity of the defect motion as compared to just noise detections \cite{Zou2015}. 
    